### 2015-08-23 manuscript/content/related.tex
Small change, much more tomorrow.

There is much research being done in the detection, prediction, or calculation of a person's blood alcohol content. The most popular mathematical model seems to be the Widmark equation; as evidenced by its prevalence in internet search results. Posey and Mozayani discuss the Widmark equation and improvements on its use by observing 5 previously published models and one new model for BAC prediction (clarify!! point?) \cite{Posey:2007}. Because of the type of information required, such methods are not accurate for personal use by the general public.

Current interlock systems involve a breathalyzer, but these are seen as expensive, bulky, and are not are all discreet. Recently, there have been some investigations into using transdermal ethanol sensors to directly measure intoxication level. Webster and Gabler took a look at the feasibility of using transdermal ethanol sensors with ignition interlock systems in cars. Transdermal sensing provides a more discreet way to measure BAC, but this method is accompanied by the problem of a significant lag between transdermally sensed alcohol concentration and blood alcohol concentration. The lag is predictable, but not constant and requires additional information about the drinker \cite{Webster:2007}.

>>>>

There are a few ways of approaching the problem of determining a person's blood alcohol content. One approach is to model mathematically the elimination of ethanol in the human body. In this case, the Widmark equation, published in 1932 by E.M.P. Widmark, is a very popular one, \begin{equation}
•C=\frac{A}{rW}-(\beta t)
\end{equation} where C is the BAC, r and $\beta$ are empirically determined constants, A is the mass of the consumed alcohol, and W is the body weight of the person.
	These days, there have been several improvements and variants. Douglas Posey and Ashraf Mozayani published an excellent article comparing this model using parameters determined by different researchers and discussing different models \cite{Posey:2007}. They found that the Widmark equation tends to overestimate, and that there can be significant discrepancy between the results of the different models. Despite that, they do provide a rough estimate. The problem is that these models also require a good deal of information that prohibit their use in a non-intrusive, drunkenness warning system.

Another approach to the problem is simply to directly measure the BAC, such as with the recent investigations into the use of transdermal ethanol sensors. Transdermal sensing provides a more discreet way to measure BAC, but this method is accompanied by the problem of a significant time lag between the sensed alcohol concentration and actual blood alcohol concentration. Gregory Webster and Hampton Gabler closely investigated this problem. They found that the lag is predictable, but variable, and requires additional information about the drinks taken to accurately predict \cite{Webster:2007}.
